Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-30 draft/ms_v5.tex
New Table 2
Change the format for magnitude catalog

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & \smag{} & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
        &      & \mmag{}  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
        &      & \mmag{}  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
    \hline
    $r$ & 0.45 & \smag{} & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
        &      & \mmag{}  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
        &      & \mmag{}  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
    \hline
    $i$ & 0.45 & \smag{} & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
        &      & \mmag{}  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
    \hline
    $z$ & 0.45 & \smag{} & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
        &      & \mmag{}  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
    \hline
    $y$ & 0.45 & \smag{} & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
        &      & \mmag{}  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
        &      & \mmag{}  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:psf_mag}.
        Here, the precision is described using the statistical uncertainties of 
        $\Delta\mathrm{mag}$ within a series of input magnitude bins (\smag{}). 
        The accuracy of PSF photometry in the same magnitude bin is described by the 
        mean value of $\Delta\mathrm{mag}$.
        }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & \scolor{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
            &      & \mcolor{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
            \cline{3-10}
            & 0.70 & \scolor{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
            &      & \mcolor{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
    \hline
    $(i-y)$ & 0.45 & \scolor{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
            &      & \mcolor{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
            \cline{3-10}
            & 0.70 & \scolor{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
            &      & \mcolor{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | cccccc |}
    \hline
    Filter & Seeing & Statistics & \multicolumn{6}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-9}
           & FWHM ($$\asec) &             & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & \smag{} & 0.111 & 0.156 & 0.161 & 0.152 & 0.176 & 0.196 \\
        &      & \mmag{}  & $\minus 0.060$ & $\minus 0.036$ & $\minus 0.004$ & 0.021 & 0.009 & $\minus 0.005$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.137 & 0.161 & 0.138 & 0.147 & 0.181 & 0.202 \\
        &      & \mmag{}  & 0.018 & $\minus 0.008$ & 0.029 & 0.040 & 0.028 & 0.012 \\
    \hline
    $r$ & 0.45 & \smag{} & 0.197 & 0.151 & 0.147 & 0.167 & 0.179 & 0.211  \\
        &      & \mmag{}  & $\minus0.036$ & $\minus 0.015$ & 0.033 & 0.033 & 0.017 & 0.012  \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.167 & 0.119 & 0.142 & 0.168 & 0.189 & 0.232 \\
        &      & \mmag{}  & $\minus 0.024$ & 0.023 & 0.050 & 0.036 & 0.025 & 0.022 \\    
    \hline
    $i$ & 0.45 & \smag{} & 0.173 & 0.157 & 0.154 & 0.168 & 0.183 & 0.218 \\
        &      & \mmag{}  & $\minus 0.023$ & 0.008 & 0.004 & 0.017 & $\minus 0.001$ & $\minus 0.006$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.154 & 0.157 & 0.153 & 0.174 & 0.193 & 0.246 \\
        &      & \mmag{}  & 0.017 & 0.043 & 0.040 & 0.021 & 0.003 & $\minus 0.013$ \\
    \hline
    $z$ & 0.45 & \smag{} & 0.171 & 0.176 & 0.165 & 0.182 & 0.201 & 0.241 \\
        &      & \mmag{}  & $\minus0.006$ & 0.042 & 0.038 & 0.018 & $\minus 0.002$ & $\minus 0.012$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.168 & 0.155 & 0.167 & 0.185 & 0.222 & 0.278 \\
        &      & \mmag{}  & 0.027 & 0.046 & 0.045 & 0.028 & 0.009 & $\minus 0.034$ \\    
    \hline
    $y$ & 0.45 & \smag{} & 0.179 & 0.169 & 0.178 & 0.197 & 0.241 & 0.308 \\
        &      & \mmag{}  & 0.011 & 0.056 & 0.044 & 0.014 & $\minus 0.067$ & $\minus 0.244$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.169 & 0.164 & 0.169 & 0.194 & 0.253 & 0.315 \\
        &      & \mmag{}  & 0.041 & 0.052 & 0.048 & 0.020 & $\minus 0.057$ & $\minus 0.299$ \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:cmodel_mag}.
        Other details are the same with Table \ref{tab:psfmag}.}
        \label{tab:cmodelmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    %\begin{tabular}{| c | c | c | cccccc |}
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline \hline
    \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
    \hline 
    \rowcolor[gray]{1.0} 21.0 & \scolor{} &   0.080 & 0.059 &   0.062 &   0.040 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
    \hline
    \rowcolor[gray]{.85} 22.0 & \scolor{} &   0.089 & 0.072 &   0.071 &   0.059 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 23.0 & \scolor{} &   0.105 & 0.090 &   0.109 &   0.103 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 24.0 & \scolor{} &   0.136 & 0.127 &   0.175 &   0.170 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 25.0 & \scolor{} &   0.179 & 0.185 &   0.227 &   0.241 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} colors using 
        $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.
        Other details are the same with Table \ref{tab:psfcolor}.
    }
        \label{tab:cmodelcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
    \hline
    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
    \cline{2-12}
    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
    \hline

    \rowcolor[gray]{.85} 19.0 & \smag{} & 0.016 & 0.016  & 0.021 & 0.026 & 0.015 & 0.012 & 0.011 & 0.019 & 0.017 & 0.019 \\
    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.008  & 0.011 & 0.009 & 0.002 & 0.001 & 0.002 & 0.003 & 0.006 & 0.007 \\
    \hline

    \rowcolor[gray]{1.0} 20.0 & \smag{} & 0.017 & 0.018  & 0.023 & 0.029 & 0.015 & 0.013 & 0.013 & 0.020 & 0.017 & 0.019 \\
    \rowcolor[gray]{1.0}      & \mmag{} & 0.009 & 0.006  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.003 & 0.006 & 0.008 \\
    \hline

    \rowcolor[gray]{.85} 21.0 & \smag{} & 0.019 & 0.019  & 0.024 & 0.031 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.023 \\
    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.006  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.006 & 0.008 \\
    \hline

    \rowcolor[gray]{1.0} 22.0 & \smag{} & 0.023 & 0.021  & 0.025 & 0.034 & 0.018 & 0.016 & 0.016 & 0.024 & 0.033 & 0.037 \\
    \rowcolor[gray]{1.0}      & \mmag{} & 0.009 & 0.005  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.004 & 0.006 & 0.006 \\
    \hline

    \rowcolor[gray]{.85} 23.0 & \smag{} & 0.029 & 0.026  & 0.027 & 0.041 & 0.020 & 0.022 & 0.025 & 0.038 & 0.074 & 0.077 \\
    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.004  & 0.012 & 0.009 & 0.002 & 0.002 & 0.003 & 0.005 & 0.000 & 0.003 \\
    \hline

    \rowcolor[gray]{1.0} 24.0 & \smag{} & 0.043 & 0.039  & 0.035 & 0.054 & 0.030 & 0.043 & 0.053 & 0.071 &   0.138 &   0.153 \\
    \rowcolor[gray]{1.0}      & \mmag{} & 0.007 & 0.003  & 0.011 & 0.006 & 0.002 & 0.001 & 0.005 & 0.003 & \n0.001 & \n0.034 \\
    \hline

    \rowcolor[gray]{.85} 25.0 & \smag{} &   0.078 &   0.091  & 0.064 & 0.090 & 0.047 &   0.050 &   0.094 &   0.104 & -- & -- \\
    \rowcolor[gray]{.85}      & \mmag{} & \n0.003 & \n0.002  & 0.011 & 0.001 & 0.003 & \n0.012 & \n0.001 & \n0.010 & -- & -- \\
    \hline

    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:psf_mag}.
        Here, the precision is described using the statistical uncertainties of 
        $\Delta\mathrm{mag}$ within a series of input magnitude bins (\smag{}). 
        The accuracy of PSF photometry in the same magnitude bin is described by the 
        mean value of $\Delta\mathrm{mag}$.
        }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.021 &   0.019 &   0.019 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.008 &   0.004 & \n0.004 & \n0.006 \\
    \hline 
    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.026 &   0.025 &   0.020 &   0.020 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.037 &   0.033 &   0.022 &   0.021 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.005 &   0.002 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.054 &   0.051 &   0.031 &   0.031 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.003 &   0.001 & \n0.001 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.077 &   0.075 &   0.058 &   0.057 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.002 & \n0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.105 &   0.105 &   0.109 &   0.123 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.009 & \n0.002 &   0.011 & \n0.002 \\
    \hline
    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.117 &   0.137 &   0.189 &   0.221 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.005 &   0.007 &   0.064 & \n0.063 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
    \hline
    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
    \cline{2-12}
    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
    \hline

    \rowcolor[gray]{.85} 20.0 & \smag{} &   0.111 & 0.137  &   0.197 &   0.167 &   0.173 & 0.154 &    0.171 & 0.168 & 0.179 & 0.169 \\
    \rowcolor[gray]{.85}      & \mmag{} & \n0.006 & 0.018  & \n0.036 & \n0.024 & \n0.023 & 0.017 & \n0.006 & 0.027 & 0.011 & 0.041 \\
    \hline

    \rowcolor[gray]{1.0} 21.0 & \smag{} &   0.156 &   0.161  &   0.151 & 0.119 & 0.157 & 0.157 & 0.176 & 0.155 & 0.169 & 0.164 \\
    \rowcolor[gray]{1.0}      & \mmag{} & \n0.036 & \n0.008  & \n0.015 & 0.023 & 0.008 & 0.043 & 0.043 & 0.046 & 0.056 & 0.052 \\
    \hline

    \rowcolor[gray]{.85} 22.0 & \smag{} & 0.019 & 0.019  & 0.024 & 0.031 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.023 \\
    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.006  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.006 & 0.008 \\
    \hline

    \rowcolor[gray]{1.0} 23.0 & \smag{} &   0.161 & 0.138  & 0.147 & 0.167 & 0.168 & 0.174 & 0.182 & 0.185 & 0.197 & 0.194 \\
    \rowcolor[gray]{1.0}      & \mmag{} & \n0.004 & 0.029  & 0.033 & 0.033 & 0.036 & 0.021 & 0.018 & 0.028 & 0.014 & 0.020 \\
    \hline

    \rowcolor[gray]{.85} 24.0 & \smag{} & 0.176 & 0.181  & 0.179 & 0.189 &   0.183 & 0.193 &   0.201 & 0.222 &   0.241 &   0.253 \\
    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.028  & 0.028 & 0.025 & \n0.001 & 0.003 & \n0.002 & 0.009 & \n0.067 & \n0.057 \\
    \hline

    \rowcolor[gray]{1.0} 25.0 & \smag{} &   0.196 & 0.202  & 0.211 & 0.232 &   0.218 &   0.246 &   0.241 &   0.278 &   0.308 &   0.315 \\
    \rowcolor[gray]{1.0}      & \mmag{} & \n0.005 & 0.012  & 0.012 & 0.022 & \n0.006 & \n0.013 & \n0.012 & \n0.034 & \n0.224 & \n0.299 \\
    \hline

    \end{tabular}
    %% -------------------------------------------------------------------------------- %%

    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:cmodel_mag}.
        Other details are the same with Table \ref{tab:psfmag}.}
        \label{tab:cmodelmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
    \hline 
    \rowcolor[gray]{1.0} 21.0 & \scolor{} &   0.080 & 0.059 &   0.062 &   0.040 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
    \hline
    \rowcolor[gray]{.85} 22.0 & \scolor{} &   0.089 & 0.072 &   0.071 &   0.059 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 23.0 & \scolor{} &   0.105 & 0.090 &   0.109 &   0.103 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 24.0 & \scolor{} &   0.136 & 0.127 &   0.175 &   0.170 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 25.0 & \scolor{} &   0.179 & 0.185 &   0.227 &   0.241 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} colors using 
        $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.
        Other details are the same with Table \ref{tab:psfcolor}.
    }
        \label{tab:cmodelcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%
